Six steps to a better relationship with your future self.

### 2011-03-26 workflow.Rnw
Fixed typos.

The first author convenes a three way video conference with the other
collaborators during his homeward commute after putting his flying car
in auto-drive mode.\footnote{One assumes that video chatting during
  manual driving of flying cars will have been outlawed in his state
  by 2020.} The group must go back to the analyses. Which ones?  The
ones from 2011?  Or 2012? Or 2018? Where are the files? The next day,
one member of the group who has kept some hard-drives around out of
nostalgia finds some of the files.\footnote{This is the same guy who
  still owns cassette tapes and compact discs.} Now
re-analyses should be easy. Right? The student, now professor, should
remember the reason for those bits of code (or at least should
remember which series of mouse clicks were used to produce the numbers
for that crucial table as it was done in 2011 \ldots or was it
2015?). Right? And, of course, the way Microsoft
Word/Stata/SPSS/R/LISREL understands files and the way that 
machines in 2021 read and write them is the same --- since Windows and
Mac OS X have always existed and will always continue to exist more or
less as they currently exist. Right? And the group knows exactly which
bit of code produced which table and which figure, right? And they
wrote their code following Nagler's Maxims \citep{nagler1995coding}
and King's Replication Standard \citep{king1995replication}, right?

If the collaborators find themselves say ``Wrong'' in
answer to the questions posed here then reproducing, updating, or
changing the original analyses will take a lot of time. If
reproduction is hard to do, then the reputations of the scholars will
suffer and, more importantly, world peace will have been delayed. This
essay provides some suggestions for practices that will make such
reproduction occur much more easily and quickly in the event that
famous papers require special scrutiny. Specifically, this piece aims
to amplify some of what we already ought to know
\citep{king1995replication,nagler1995coding}, and to add to some of
those ideas given current practices, platforms, and possibilities.

@@

\subsection{Code to communicate: Comment your code.}
Comments --- unexecuted text inside of a script --- are a message to
collaborators (including your future self) and other consumers of your
work. In the above code chunk, I used comments to explain the lines to
readers unfamiliar with R and to remember that I had tried a different
specification but decided not to use it because adding the squared
term did not really change the substantive story arising from the
model.\footnote{R considers text marked with \Verb+#+ as a comment.}
Messages left for your future self (or near-future others) help
retrace and justify your decisions as the work moves from seminar
paper to conference paper to poster back to paper to dissertation and
onwards.

@@

Literate data analysis is not the same as Sweave, even if Sweave is a
nice implementation.\footnote{The R project has a task view devoted to
  \href{http://cran.r-project.org/web/views/ReproducibleResearch.html}{reproducible
    research} listing many of the different approaches to literate
  programming for R.}  \href{http://www.lyx.org/}{LyX} offers a
WYSIWYG environment for \LaTeX~ that supports Sweave. And the
\Verb+odfWeave+ package in R allows the use of OpenOffice documents in
exactly the same way.\footnote{A quick Google search of ``Sweave for
  Stata'' turned up lots of resources for literate programming with
  Stata.} If your workflow does not involve \LaTeX~ and R, you can
still implement some of the principles here. Imagine creating a style
in Microsoft Word called ``code'' which hides your code when you print
your document, but which allows you do at least run each code chunk
piece by piece [or perhaps there are ways to extract all text of style
``code'' from a Microsoft Word document]. Or imagine just using some
other kind of indication linking paragraphs to specific places in code
files. There are many ways that creative people can program in a
literate way.

@@

Where should one store data files? Anobvious solution is always to
make sure that the data file used by a command file is in the same
directory as the command file. More elegant solutions require all
co-authors to have the same directory structure so that
\Verb+load('Data/thedata.rda')+ means the same thing on all computers
used to work on the project. This kind of solution is one of the
things that formal version control systems do well (as discussed
a bit more in \S\ref{sec:vers-contr-prev}).

@@

\paragraph{Step \thesection} We should know data where the data came from and
what operations were performed on which set of data.

@@

But what if the UN never hears of your work, or, by some cruel fate, that your
article does not spawn debate? Why then would you spend time to
communicate with your future self and others? My own answer to this
question is that I want my work to be credible and useful to myself
and other scholars even if each article does not immediately change
the world.  What I report in my data analyses should have two main
characteristics: (1) the findings of the work should not be a matter
of opinion; and (2) other people should be able to reproduce the findings. That is,
the work represents a shared
experience --- and an experience shared without respect to the
identities of others (although requiring some common technical
training and research resources).
% Such work should make us change how
% we act --- or at least, it ought to stand on stronger epistemological
% ground than other claims about experiences which ought to be shared or
% shareable.

>>>>

The first author convenes a three way video conference with the other
collaborators during his homeward commute after putting his flying car
in auto-drive mode.\footnote{One assumes that video chatting during
  manual driving of flying cars will have been outlawed in his state
  by 2020.} The group must go back to the analyses. Which ones?  The
ones from 2011?  Or 2012? Or 2018? Where are the files? The next day,
one member of the group who has kept some hard-drives around out of
nostalgia finds some of the files.\footnote{This is the same guy who
  still owns cassette tapes and compact discs.} Now
re-analysis should be easy. Right? The student, now professor, should
remember the reason for those bits of code (or at least should
remember which series of mouse clicks were used to produce the numbers
for that crucial table as it was done in 2011 \ldots or was it
2015?). Right? And, of course, the way Microsoft
Word/Stata/SPSS/R/LISREL understands files and the way that 
machines in 2021 read and write them is the same --- since Windows and
Mac OS X have always existed and will always continue to exist more or
less as they currently exist. Right? And the group knows exactly which
bit of code produced which table and which figure, right? And they
wrote their code following Nagler's Maxims \citep{nagler1995coding}
and King's Replication Standard \citep{king1995replication}, right?

If the collaborators find themselves saying ``Wrong'' in
answer to the questions posed here then reproducing, updating, or
changing the original analyses will take a lot of time. If
reproduction is hard to do, then the reputations of the scholars will
suffer and, more importantly, world peace will have been delayed. This
essay provides some suggestions for practices that will make such
reproduction occur much more easily and quickly in the event that
famous papers require special scrutiny. Specifically, this piece aims
to amplify some of what we already ought to know
\citep{king1995replication,nagler1995coding}, and to add to some of
those ideas given current practices, platforms, and possibilities.

@@

\subsection{Code to communicate: Comment your code.}
Comments --- unexecuted text inside of a script --- are a message to
collaborators (including your future self) and other consumers of your
work. In the above code chunk, I used comments to explain the lines to
readers unfamiliar with R and to remember that I had tried a different
specification but decided not to use it because adding the squared
term did not really change the substantive story arising from the
model.\footnote{R considers text marked with \texttt{\#} as a comment.}
Messages left for your future self (or near-future others) help
retrace and justify your decisions as the work moves from seminar
paper to conference paper to poster back to paper to dissertation and
onwards.

@@

Literate data analysis is not the same as Sweave, even if Sweave is a
nice implementation.\footnote{The R project has a task view devoted to
  \href{http://cran.r-project.org/web/views/ReproducibleResearch.html}{reproducible
    research} listing many of the different approaches to literate
  programming for R.}  \href{http://www.lyx.org/}{LyX} offers a
WYSIWYG environment for \LaTeX~ that supports Sweave. And the
\Verb+odfWeave+ package in R allows the use of OpenOffice documents in
exactly the same way.\footnote{A quick Google search of ``Sweave for
  Stata'' turned up lots of resources for literate programming with
  Stata.} If your workflow does not involve \LaTeX~ and R, you can
still implement some of the principles here. Imagine creating a style
in Microsoft Word called ``code'' which hides your code when you print
your document, but which allows you to at least run each code chunk
piece by piece [or perhaps there are ways to extract all text of style
``code'' from a Microsoft Word document]. Or imagine just using some
other kind of indication linking paragraphs to specific places in code
files. There are many ways that creative people can program in a
literate way.

@@

Where should one store data files? An obvious solution is always to
make sure that the data file used by a command file is in the same
directory as the command file. More elegant solutions require all
co-authors to have the same directory structure so that
\Verb+load('Data/thedata.rda')+ means the same thing on all computers
used to work on the project. This kind of solution is one of the
things that formal version control systems do well (as discussed
a bit more in \S\ref{sec:vers-contr-prev}).

@@

\paragraph{Step 3} We should know where the data came
from and what operations were performed on which set of data.

@@

But what if the UN never hears of your work, or, by some cruel fate, your
article does not spawn debate? Why then would you spend time to
communicate with your future self and others? My own answer to this
question is that I want my work to be credible and useful to myself
and other scholars even if each article does not immediately change
the world.  What I report in my data analyses should have two main
characteristics: (1) the findings of the work should not be a matter
of opinion; and (2) other people should be able to reproduce the findings. That is,
the work represents a shared
experience --- and an experience shared without respect to the
identities of others (although requiring some common technical
training and research resources).
% Such work should make us change how
% we act --- or at least, it ought to stand on stronger epistemological
% ground than other claims about experiences which ought to be shared or
% shareable.
